Visualization and analysis of probability distributions of large temporal data

### 2021-11-10 Rmd/01-intro.Rmd
minor changes in abstract and intro

Chapter \@ref(ch:gravitas) describes classes of time deconstructions using linear and cyclic time granularities, which can be used to create data visualizations to explore periodicities, associations, and anomalies. It provides a formal characterization of cyclic granularities which can be circular (such as hour-of-the-day), quasi-circular (such as day-of-the-month), and aperiodic (public holidays). It further facilitates manipulation of single- and multiple-order-up time granularities through cyclic calendar algebra, as well as provides a recommendation algorithm to check the feasibility of creating plots for any two cyclic granularities. Our proposed method is also applicable to non-temporal hierarchical granularities with an underlying ordered index. The methods are implemented in the open-source R package `gravitas` and are consistent with a tidy workflow [@wickham2016r], with probability distributions examined using the range of graphics available in `ggplot2`[@Wickham2009pk].

>>>>

Chapter \@ref(ch:gravitas) describes classes of time deconstructions using linear and cyclic time granularities, which can be used to create data visualizations to explore periodicities, associations, and anomalies. It provides a formal characterization of cyclic granularities and facilitates manipulation of single- and multiple-order-up time granularities through cyclic calendar algebra, as well as provides a recommendation algorithm to check the feasibility of creating plots for any two cyclic granularities. Our proposed method is also applicable to non-temporal hierarchical granularities with an underlying ordered index. The methods are implemented in the open-source R package `gravitas` and are consistent with a tidy workflow [@wickham2016r], with probability distributions examined using the range of graphics available in `ggplot2`[@Wickham2009pk].
